Graph Data Generators in the World of Big Data

### 2018-05-24 comparison.tex
Merging of sections 3 and 4

\section{Comparative Study}
\label{sec:comparison}

In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective applications. In particular, we show:

@@

\begin{sidewaystable}
\scriptsize 
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | l |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline               
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}             
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline                
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}               
               & \textbf{Read}
               & \textbf{Update}               
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline                
\hline   % general graphs (Angela)
\multirow{5}{*}{\rot{\textbf{General}}}
  & graph500  & fixed & & Y & N & Y & power-law & &  Y  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
\cline{2-10}
  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & Preferential Attachment~\cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline  % graph databases (Angela)
\multirow{4}{*}{\rot{\textbf{DBs}}}
 & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
 \cline{2-10}
& graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
 \cline{2-10}
 & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\hline
\hline % Semantic web (Irena)
\multirow{18}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\  
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\  
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\  
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\  
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\ 
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\ 
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\ 
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\  
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\ 
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\ 
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\ 
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\  
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\  
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\  
\cline{2-10}
 & LinkGen & & & & & & & & \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize 
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| l |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline               
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}             
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline                
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}               
               & \textbf{Read}
               & \textbf{Update}               
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline                
\hline
\hline % social networks (Arnau)
\multirow{9}{*}{\rot{\textbf{Social networks}}}
& LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
\cline{2-10}
& S3G2 & Y & Y  & N &  & Y & Facebook-like  &  CSV, RDF & Y   \\
\cline{2-10}
& SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
\cline{2-10}
& Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\cline{2-10}
& Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
\cline{2-10}
& BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\hline
\hline   % graph analytics (Sherif)
\multirow{5}{*}{\rot{\textbf{Analytics}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline   % streaming (Sherif)
\multirow{5}{*}{\rot{\textbf{Streaming}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

In Table~\ref{tab:comparisonReferences} we provide an overview of works which use the respective generator for evaluation of the proposed method or comparative study of a selected set methods. \QUE{CSUR has strict page limit 35 pages. I'm afraid that this will extend the list of references extremely.}

\begin{table}
\scriptsize
\centering
\tbl{Exploitation of the generators}{
\begin{tabular}{| l | p{11.5cm} | }
 \hline          \textbf{Generator}
               & \textbf{Cited in}
               \\ \hline
\hline  % general graphs
  & \\  
\hline
  & \\  
\hline
\hline % graph databases
  & \\  
\hline
  & \\  
\hline
\hline % Linked Data
 LUBM & \\  
\hline
 LBBM & \\  
\hline
 UOBM & \\  
\hline
 IIMB & \\  
\hline
 BSBM & \\  
\hline
 SP$^2$Bench & \\  
\hline
 DBPSB & \\  
\hline
 LODIB & \\  
\hline
 SIB & \\  
\hline
 Geographica & \\  
\hline
 WatDiv & \\  
\hline
 RBench & \\  
\hline
 LDBC SPB & \\  
\hline
\hline  % social networks
  & \\  
\hline
  & \\  
\hline
\end{tabular} }
\label{tab:comparisonReferences}
\end{table}

>>>>

\section{Classification and Comparative Study}
\label{sec:comparison}

In order to provide the reader with a quick preview of the generators and thus finding the target solutions easily, we start the survey with classification and comparative study of the existing tools. There are various ways how to classify them. We first overview approaches used in related work and then we introduce ours. As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy differs too.

In general, the graph data generators can be classified according to various criteria. Paper~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators. Given a degree distribution (typically following a power law), \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.). On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.

Paper~\cite{Chakrabarti:2006:GML:1132952.1132954} introduces five categories of graph models that can be synthesized: (1) \emph{random graph models} (e.g., Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960}) generated by a random process, (2) \emph{preferential attachment models} (e.g., Barabasi-Albert model) which try to model the power law from the preferential attachment viewpoint, (3) \emph{optimization-based models} (e.g., HOT model~\cite{PhysRevLett.84.2529}) resulting from the idea that power laws can result from resource optimizations and tolerance to risks, (4) \emph{tensor-based models} (e.g., R-MAT) targeting a trade-off between low number of model parameters and efficiency, and (5) \emph{internet-specific models} corresponding to hybrids using ideas from the other categories in order to suit the specific features of the graphs.

The type of the generator can also be influenced by the benchmark involving it, whereas we can distinguish, e.g., \emph{domain-specific} benchmarks, \emph{application-specific} benchmarks, \emph{workload-driven} benchmarks,  \emph{microbenchmarks} etc.

%\paragraph{Erd\"{o}s-R\'{e}nyi} One of the first and still very popular approaches with lots of variations and modifications is the random graph model proposed in~\cite{Erdos:1960}. Given a positive integer $n$ and a probability value $0 \leq p \leq 1$, the graph $G(n,p)$ is an undirected graph on $n$ vertices whose edges are chosen s.t. for all pairs of vertices $u,v$ there is an edge $(u,v)$ with probability $p$.
%
%\paragraph{Barabasi-Albert} The Barabasi-Albert (BA) model~\cite{Barabasi99emergenceScaling} proposes that structure emerges in network topologies as the result of two processes -- growth and preferential attachment. The BA model starts with a small set of nodes and grows the network as nodes and edges are added over time. Preferential attachment is based on the idea that the probability of connecting to a node is proportional to the current degree of that node (i.e., ``the rich get richer'').
%
%\paragraph{HOT} The highly optimized tolerance (HOT)~\cite{PhysRevLett.84.2529} model is introduced  using a ``forest fire'' example as follows: Suppose we have a forest which is prone to forest fires. Each portion of the forest has a different chance of starting the fire. We wish to minimize the damage by assigning (a limited amount of) resources such as firebreaks at different positions in the forest. More precisely, we have $n$ possible events, each with an associated probability $p_i, 1 \le i \le n$. Each event can lead to some loss $l_i$, which is a function of the resources $r_i$ allocated for that event $(l_i = f (r_i))$, whose total number is limited ($\sum_i r_i \le R$ for some given $R$). The aim is to minimize the expected cost $\sum_i p_i l_i$. The authors show that resource placement is related to the probability distribution $p_i$ by a power law and the probability of events which cause a loss greater than some value $k$ is related to $k$ by a power law too.
%
%
%\paragraph{R-MAT} The R-MAT (Recursive MATrix)~\cite{DBLP:conf/sdm/ChakrabartiZF04} model can be used to create graphs with community structure, power law degree distributions, and a small diameter. It generates weighted, directed and bipartite graphs. Graph generation is modeled with a matrix recursion procedure in which the adjacency matrix (empty at the beginning) is recursively subdivided into four equal-sized partitions and edges are distributed across the partitions with unequal probabilities.

%In Figure~\ref{fig:classification} ...
%
%\begin{figure}
%\centering
%\includegraphics[width=0.8\textwidth]{classification.png}
%\caption{Classification of graph data generators}
%\label{fig:classification}
%\end{figure}

We decided to classify the generators primarily on the basis of the respective application domains or communities. In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains. In particular, we show:

@@

As we can see...

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{8}{*}{\rot{\textbf{General}}}
  & graph500  & fixed & & Y & N & Y & power-law & &  Y  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
\cline{2-10}
  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & Preferential Attachment~\cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline %  ======================  Semantic web
\multirow{22}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & & & & & & & & \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{Graph DBs}}}
 & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
 \cline{2-10}
& graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
 \cline{2-10}
 & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\hline
\hline %  ======================   social networks
\multirow{9}{*}{\rot{\textbf{Social networks}}}
& LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
\cline{2-10}
& S3G2 & Y & Y  & N &  & Y & Facebook-like  &  CSV, RDF & Y   \\
\cline{2-10}
& SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
\cline{2-10}
& Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\cline{2-10}
& Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
\cline{2-10}
& BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\hline
\hline   % ======================   graph analytics
\multirow{5}{*}{\rot{\textbf{Analytics}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline   %  ======================  streaming 
\multirow{5}{*}{\rot{\textbf{Streaming}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}
